---
title: "SlideseqV2 hippocampus data Analysis"
author: "Ying Ma"
date: May 24, 2021
output:
  prettydoc::html_pretty:
    theme: HPSTR 
    highlight: github
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is the analysis of the mouse olfactory bulb from Spatial Transcriptomics (ST) technique. The 
 
Due to the storage issue of github, the data that are needed to run this analsyis are stored on the [google drive](https://drive.google.com/drive/folders/1wRPxn1YI7f1oUw8eC42htXMjTUqyIT1g?usp=sharing). 
set
## load the data

```{r message=FALSE, warnings=F, eval=F}
rm(list=ls())
library(SingleCellExperiment)
library(pbmcapply)
library(CARD)
### load the single cell RNA-seq data used as the reference for deconvolution
load("./Hippocampus.dge.sceset.RData")
### load the spatial data 
load("./slideseqV2.count.RData")
### set paramaters
ct.varname = "cellType"
sample.varname = "sampleInfo"
ct.select = as.character(unique(colData(sce)$cellType))
location <- cbind.data.frame(x=as.numeric(sapply(strsplit(colnames(slideseqV2),split="x"),"[",1)),y=as.numeric(sapply(strsplit(colnames(slideseqV2),split="x"),"[",2)))
rownames(location) = colnames(slideseqV2)
```

## Deconvolution with CARD
```{r eval=F,warnings=F}
##### create CARD object
CARD_obj = createCARDObject(
	sc_count = assays(sce)$counts,
	sc_meta = colData(sce),
	spatial_count = slideseqV2,
	spatial_location = location,
	ct.varname = ct.varname,
	ct.select = ct.select,
	sample.varname = sample.varname,
	minCountGene = 100,
	minCountSpot =5) 
##### delete the original file to save the memory
rm(sce)
rm(location)
rm(slideseqV2)
gc()
##### CARD deconvolution
CARD_obj = CARD_deconvolution(CARD_obj)
print(CARD_obj@Proportion_CARD[1:2,])
              Astrocyte        CA1        CA3 Cajal_Retzius    Choroid
888.95x3219.5 0.0991712 0.03364185 0.03650123    0.09582946 0.06029124
4762.2x5020.4 0.1848699 0.02340987 0.01151686    0.11039367 0.06643968
                  Denate Endothelial_Stalk Endothelial_Tip Entorihinal
888.95x3219.5 0.03576194        0.01516197      0.02458487  0.16698704
4762.2x5020.4 0.02638077        0.02124969      0.02608303  0.08141408
               Ependymal Interneuron Microglia_Macrophages      Mural
888.95x3219.5 0.01126246  0.13054963            0.02372019 0.03194189
4762.2x5020.4 0.01866272  0.09362967            0.01305731 0.03856378
              Neurogenesis Neuron.Slc17a6 Oligodendrocyte Polydendrocyte
888.95x3219.5   0.02822858     0.11863522      0.06500265     0.02272858
4762.2x5020.4   0.03033911     0.06998887      0.15760321     0.02639780
```

## Construact a refined spatial map by CARD
```{r eval=F,warnings=F}
##### For example, we set the initial number of grids to be 2000
##### There are some locations that are outside of the main circle of the tissue, we should exclude them to avoid its impact on the tissue shape detection
exclude = c("1209.9x5751.6","932.04x5567.2","221.35x4978.6","803.66x4850.6","371.65x4474.5","252.32x2760.2",
            "341.18x2331.2","157.22x1996.2","465.7x1602","1435.2x270.75","2100.8x501.66","2211.5x153.96",
            "3853.4x215.24","5414.3x970.87","1339.1x5019.2","1541.6x5370.7","1536.8x5341.8","1508.8x5254.6",
            "1498.4x5244.1","1593.6x5155.4","1607x5144.9","1651.8x5064.9","1481.5x5229.1","1496x5223.5",
            "1508.4x5212.2","1522.7x5210.5","685.08x5145.3","1518.8x5225.6")
CARD_obj = CARD.imputation(CARD_obj,NumGrids = 10000,ineibor = 10,exclude = exclude)## print output
print(CARD_obj@refined_prop[1:2,])
         Astrocyte        CA1        CA3 Cajal_Retzius    Choroid     Denate
3022x786 0.1080091 0.05208850 0.02684785    0.10101177 0.03268236 0.06272963
3070x786 0.1130811 0.05296805 0.06285999    0.08734442 0.03575684 0.06352145
         Endothelial_Stalk Endothelial_Tip Entorihinal  Ependymal Interneuron
3022x786        0.02115726      0.02742217  0.08552018 0.00697323  0.07848406
3070x786        0.01632546      0.03008589  0.08778664 0.01629819  0.05780146
         Microglia_Macrophages      Mural Neurogenesis Neuron.Slc17a6
3022x786            0.01245631 0.03108299   0.03949124      0.1005717
3070x786            0.04920186 0.03598855   0.03361353      0.1025258
         Oligodendrocyte Polydendrocyte
3022x786       0.1937261     0.01974551
3070x786       0.1307404     0.02410037