---
title: "Mouse Olfactory Bulb Analysis"
author: "Ying Ma"
date: April 24, 2022
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is the analysis of the mouse olfactory bulb from Spatial Transcriptomics (ST) technique. The 
 
Due to the storage issue of github, both the scRNASeq reference data and mouse olfactory bulb ST dataset are stored on the [google drive](https://drive.google.com/drive/folders/1wRPxn1YI7f1oUw8eC42htXMjTUqyIT1g?usp=sharing). 

## load the data

```{r message=FALSE, warnings=F, eval=T}
rm(list=ls())
library(SingleCellExperiment)
library(pbmcapply)
library(CARD)
### load the single cell RNA-seq data used as the reference for deconvolution
load("./MOB.dge.sceset.RData")
### load the spatial data 
load("./Rep12_MOB_count_matrix-1.RData")
### set paramaters
ct.varname = "cellType"
sample.varname = "sampleInfo"
ct.select = as.character(unique(colData(sce)$cellType))
location <- cbind.data.frame(x=as.numeric(sapply(strsplit(colnames(MOB_raw),split="x"),"[",1)),y=as.numeric(sapply(strsplit(colnames(MOB_raw),split="x"),"[",2)))
rownames(location) = colnames(MOB_raw)
```

## Deconvolution with CARD
```{r eval=T,warnings=F}
##### create CARD object
CARD_obj = createCARDObject(
	sc_count = assays(sce)$counts,
	sc_meta = colData(sce),
	spatial_count = MOB_raw,
	spatial_location = location,
	ct.varname = ct.varname,
	ct.select = ct.select,
	sample.varname = sample.varname,
	minCountGene = 100,
	minCountSpot =5) 
##### CARD deconvolution
CARD_obj = CARD_deconvolution(CARD_obj)
print(apply(CARD_obj@Proportion_CARD,2,summary))
```

## Construact a refined spatial map by CARD
```{r eval=T,warnings=F}
##### For example, we set the initial number of grids to be 2000
CARD_obj = CARD.imputation(CARD_obj,NumGrids = 2000,ineibor = 10,exclude = NULL)## print output
print(apply(CARD_obj@refined_prop,2,summary))
